Difference-in-Differences with Spatial Spillovers

### 2023-06-10 latex/slides/Spillover_slides.tex
Updated Slides

        \item Discuss estimation of effects that are \emph{robust} to spillovers

@@

    \onslide<1->{
        The canonical difference-in-differences estimate is: 
        \only<1>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Counterfactual Trend}}
            \]
        }
        \only<2>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{coral} Spillover on Control}}}
            \]
        }
        \only<3>{
            \[ 
                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\substack{\text{Counterfactual Trend} \ + \ \tau \\[2mm] \ + \ \text{\color{kelly} Spillover on Treated}}} - 
                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{coral} Spillover on Control}}}
            \]
        }
    }

    Two problems occur in the presence of spillover effects:

    \begin{itemize}
        \onslide<2->{
            \item {\bf \color{coral} Spillover onto Control Units:} Nearby ``control'' units fail to estimate counterfactual trends
        }

        \onslide<3->{
            \vspace{2.5mm}
            \item {\bf \color{kelly} Spillover onto other Treated Units:} Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
        }
    \end{itemize}

% \begin{frame}{Remove Bias}
%     \only<1>{
%         \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
%     }
%     \only<2>{
%         \[ 
%             y_{it} = \mu_t + \mu_i + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} S_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} S_{it} * D_{it}} +  + \varepsilon_{it}
%         \]
%     }

%     \only<1>{ 
%         \[ 
%             \mathbb{E}[\hat{\tau}] = \tau + \text{\color{coral} Spillover on Control} + \text{\color{kelly}Spillover on Treated}
%         \]
%     }
%     \only<2>{
%         \[ 
%             \mathbb{E}[\hat{\tau}] = \tau,
%         \]
%         so long as $S_{it}$ contains all the units with spillovers.
%     }
% \end{frame}

% \begin{frame}
%     \begin{figure}[tb!]
%         \caption{Single Ring - Removes spillover effects}
%         \begin{center}
%             \resizebox{0.9\textwidth}{!}{
%                 \includegraphics{../../figures/figure-within_example.pdf}
%             }
%         \end{center}
%     \end{figure}
% \end{frame}

% \begin{frame}
%     \begin{figure}[tb!]
%         \caption{Multiple Rings - Improves estimation of spillover effects}
%         \begin{center}
%             \resizebox{0.9\textwidth}{!}{
%                 \includegraphics{../../figures/figure-rings_example.pdf}
%                 } 
%             \end{center}
%     \end{figure}
% \end{frame}

% \begin{frame}
%     \begin{figure}[tb!]
%         \caption{Community Health Centers}
%         \begin{center}
%             \resizebox{0.9\textwidth}{!}{
%                 \includegraphics{../../figures/figure-chc-es_combined_slides.pdf}
%                 } 
%             \end{center}
%     \end{figure}
% \end{frame}

@@

        \begin{itemize}
            \vspace{2.5mm}
            \item I decompose the difference-in-differences estimator into three parts: Direct Effect of Treatment, Spillover onto Treated Units, Spillover onto Control Units

            \vspace{2.5mm}
            \item Discuss estimands of interest and classify which are identifiable and which are not
        \end{itemize}

@@

\begin{frame}{Estimands}{Switching Effect}
    \[
        \textcolor{maroon}{\tau_{\text{switch}}(h)} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})) \mid D_i = 1, h_i(\vec{D}) = h \right]
    \]

@@

\begin{frame}{Estimands}{Switching Effect}
    \begin{align*}
        \textcolor{maroon}{\tau_{\text{switch}}(h)} &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]\\ 
        &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]} 
    \end{align*}

>>>>

        \item Discuss estimation of effects in the presence of spillovers

@@

  The canonical difference-in-differences estimate is: 
  \only<1>{
      \[ 
          \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
          \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Counterfactual Trend}}
      \]
  }
  \only<2>{
      \[ 
          \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
          \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{coral} Spillover on Control}}}
      \]
  }
  \only<3>{
      \[ 
          \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\substack{\text{Counterfactual Trend} \ + \ \tau \\[2mm] \ + \ \text{\color{kelly} Spillover on Treated}}} - 
          \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{coral} Spillover on Control}}}
      \]
  }

  \only<1>{Use the control units to estimate what the treated units' trends would have been without treatment}
  \only<2-3>{
    \noindent Two problems occur in the presence of spillover effects:
    \begin{itemize}
        \item {\bf \color{coral} Spillover onto Control Units:} Nearby ``control'' units fail to estimate counterfactual trends

        \only<3>{
            \item {\bf \color{kelly} Spillover onto other Treated Units:} Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
        }
    \end{itemize}
  }
\end{frame}

@@

        \begin{itemize}
            \vspace{2.5mm}
            \item I focus on non-parametric identification conditions

            \vspace{2.5mm}
            \item Discuss estimands of interest and classify identification for each
        \end{itemize}

@@

\begin{frame}{Estimands}{Switching Effect}
    \[
        \textcolor{purple}{\tau_{\text{switch}}(h)} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})) \mid D_i = 1, h_i(\vec{D}) = h \right]
    \]

@@

\begin{frame}{Estimands}{Switching Effect}
    \begin{align*}
        \textcolor{purple}{\tau_{\text{switch}}(h)} &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]\\ 
        &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]} 
    \end{align*}
